### 2021-06-29 letter/responseLetter.tex

\vspace{0.2cm}

\item Another point to improve is connected to the implications of the study. While the paper discusses in nice way the 
results achieved, it does not provide a clear view of how those results can be potentially useful for researchers 
working on Android sandboxes as well as what are the next steps that the research community should pursue to 
improve the detection of malware.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} To mitigate this issue, we reviewed our Section 4 (Results) and created a new Section 5 (Implications), which present how our results can be useful for both researchers and practitioner. Thanks for this observation.}

@@

\vspace{0.2cm}

\item Last but not least, the threats to validity section should be improved, by commenting on conclusion and construct validity.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for this observation. We reviewed our Threats to Validity section according to
  a \emph{threats to validity} taxonomy for this kind of study~\cite{10.5555/2349018}. The current version
  of the paper includes specific sections addressing Conclusion Validity, Internal Validity, External
Validity, and Construct Validity.}

@@

\begin{itemize}

\item The abstract is not clear. First, the context if not well addressed.
  For example, why ``mining Android sandboxes'' is important? I had to read
  several related reference at the beginning to understand it. Second, it is not common practice to 
include reference in abstract. However, I reserve my opinion since I know it may be preferred by some researchers.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for raising these questions. We reviewed the abstract
  to better explain the relevance of the mining sandbox approach. As a short answer,
  literature reports show that the mining sandbox approach is effective  not only to prevent malicious
  calls to sensitive APIs but also to classify a version of an Android application as a malware.}

### 2021-06-30 introduction.tex
Update introduction.tex
Remove Krishina comments.

The lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that explores the performance of dynamic analysis for identifying malicious behavior using the mining sandbox approach.  %\kn{The use of word same here makes me wonder if readers could be confused. IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right? Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}
Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malicious version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps). As we discuss in this paper, this DroidFax static analysis component leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work. In the security domain, overestimating the performance of a technique for malware identification brings serious risks, and we show here that DroidFax inflated significantly the performance of the dynamic analysis tools for mining sandboxes, as reported in the \blls.

@@

%% In summary, our current study differs fromthe original work in three aspects:

%% \begin{enumerate}[(a)]
%%   \item We isolate the effect of the static analysis component of DroidFax.
%%    \item We included a fake test
%% case generation tool (named \joke). \joke simulates a test tool that does not execute Android apps during DroidXP execution, disregarding the effects of dynamic analysis, and computing the results with only static analysis DroidFax component.
%% \item We extend the execution time and the number of executions of each test case generator tool for all apps
%% in our dataset.

%% \end{enumerate}
%% where offers direct access to all source code, installation process, dependencies, and how to run. We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20}, and here we discuss the results of a broader investigation that also uses DroidXP to explain the performance of static and dynamic analysis approaches for mining sandboxes. Our goal is to understand how static analysis algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. This work is an extension of SCAM 2020 paper, since that for our actual study, we had to adapt DroiXP to allow it to isolate the effects of static analysis component of DroidFax, and take into account this effect at our analysis.

%% Our research work presents the results of two empirical studies that aim to
%% address our research goal. In the
%% first study, we conduct a replication of the \blls, as presented at {\color{red}SCAN 2020} conference~\cite{DBLP:conf/scam/CostaMCMVBC20}, though

>>>>

The lack of understanding about static and dynamic analysis complementing each other also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that explores the performance of dynamic analysis for identifying malicious behavior using the mining sandbox approach. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malicious version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps). As we discuss in this paper, this DroidFax static analysis component leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work. In the security domain, overestimating the performance of a technique for malware identification brings serious risks, and we show here that DroidFax inflated significantly the performance of the dynamic analysis tools for mining sandboxes, as reported in the \blls.

@@
